---
title: "In Class"
output: html_document
---

```{r setup, include=FALSE}
library('tidyverse')
library('ranger') # install.packages('ranger')
library("wru") # install.packages('wru') # Bayesian prediction of ethnicity

# Random seed
set.seed(123)

# Custom function
`%not in%` <- function (x, table) is.na(match(x, table, nomatch=NA_integer_))
```


What is the data set?  

  - Using `data/train.csv` only, because we are not testing on Kaggle. <https://www.kaggle.com/c/titanic/data>
```{r}
dat = read_csv('data/train.csv')
head(dat)
```


We are looking to predict `Survival` in order to see what variables may lead to people who survived the crash. Follow along: <https://tylerburleigh.com/blog/surviving-the-titanic-with-r-caret/>


EDA: 
  - Look for `NA`
  - Decide on how they should be handled
  - Make plots
  - Create new features (if it makes sense)  
  
```{r}

```


Select variables
```{r}

```



Create test / train split
```{r}

```



Build **decision tree** model with `caret` and `rpart`
```{r}

```




