---
title: "In Class"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library('tidyverse')
library('rpart') #install.packages('rpart')
library('janitor')

# Random seed
set.seed(123)
```

########
######## SEE IN_CLASS_COMPLETED.RMD IN ORIGINAL REPO 
########

What is the data set?  

  - Using `data/train.csv` only, because we are not testing on Kaggle. <https://www.kaggle.com/c/titanic/data>
```{r}
dat = read_csv('data/train.csv')
head(dat)
```

```{r}
colSums(is.na(dat))
# Throw out Cabin, as 687 are NA
# Impute Age, as 117 are NA
```

```{r}
dat %>%
  group_by(Survived, Age) %>%
  count() %>%
  ggplot(aes(x = Age)) +
  geom_histogram()

#Check how much Age and Survival are correlated
dat %>%
  ggplot(aes(x = factor(Survived), y= Age)) +
  geom_boxplot()
```

#TODO Items:
  - Remove Cabin....majority missing
  - Impute Age
  = Remove Passenger id
  - ? used name for "Last name" only or title
  - Remove ticket number - not standariez
  - Embarked use mode to impute
  

```{r}
dat %>%
  group_by(Name) %>%
  count() %>%
  arrange(-n)
``` 


We are looking to predict `Survival` in order to see what variables may lead to people who survived the crash. 

EDA: 
  - Look for `NA`
  - Decide on how they should be handled
  - Make plots
  - Create new features (if it makes sense)  
```{r}
dat  %>%
  group_by(Survived) %>%
  summarize(n = n()) %>%
  mutate(n_pct  = n / sum(n))
```
  
```{r}
dat %>%
  # group_by(Survived) %>%
  ggplot(aes(x=factor(Pclass),y=Age)) +
  geom_boxplot()

dat %>%
  group_by(Survived) %>%
  ggplot(aes(x=Pclass)) +
  geom_bar()

dat %>%
  group_by(Pclass) %>%
  count() %>%
  arrange(-n)
```


Select variables
```{r}
dat_trimmed <- dat %>%
  select(-Cabin, -Ticket, -PassengerId)

#Impune each split TEST/TRAIN because we're using mode to fill in NAs in Embarked
dat %>%
  group_by(Embarked) %>%
  count()

dat_clean = dat %>%
  mutate(
    Embarked = if_else(is.na(Embarked), mode(Embarked), Embarked)
  )
  
```



Create test / train split
```{r}

```



Build **decision tree** model with `caret` and `rpart`
```{r}

```




